The Accuracy of KNN, decision tree, random forest, SVM, neural network, naive Bayes classifier and PLA for early Prediction of Diabetes

### 2023-04-05 hw1/paper/main.tex
update experiment result and modify the section of naive Bayes classifier

  \bf{neural network}: \rm{Neural} network have been used in many fields to deal with intricate datas.With input layer, hidden layer and output layer constructed by neurons, each data in dataset is processed while passing through neurons, layer by layer.After the processing, the outcome can be used to predict.Using back propogation, the accuracy of predictions increase in each training.In order to construct the hidden layer more efficient, NAS(Neural Arcitecture Searching) is used to search suitable structure for hidden layer, increasing the accuracy.According to \cite{Gadekallu2020}\cite{Beghriche2021}, many neural network have been constructed and trained already, with high efficiency and accuracy in prediction of diabetes.

  \bf{naive Bayes classifier}:

@@

\section{decision tree}
  Given a dataset, $D$, which contains $N$ data and class label, the construction of a decision tree can be described as 
  below: suppose there are $M$ candidate decisions, denoted $f_i$. A decision can separate dataset $D$ into $m$ kinds, denote 
  $D'_j$. The decision tree will adopt $\arg\max_{f} G(D, f)=I(D)-\sum^m_{j=1}\frac{N'_j}{N}I(D'_j)$ as node decision, 
  and then recursively construct the tree until the data in separated dataset have the same class label. 
  When a data with unknown class label comes, a decision tree determines recursively by the decision node until the leaf node.
  The function of calculating information, $I$, can be various from implementation. The most famous two information function is 
  entropy, and gini impurity. The formula of information entropy is $I_H(X)=-\sum_{x}p(x)\log_2p(x)$ 
  and gini impurity is $I_G(X)=1-\sum_{x}p(x)^2$.

@@

\section{SVM}
 Given a dataset $D$ containing $N$ data points and a label with a binary class label of $0$ or $1$ representing the presence or absence of diabetes, respectively. Individually project each data point in the dataset $D$ onto the hyperplane, we can obtain a point $(X_{i1}, X_{i2}, ..., X_{ij}, ..., X_{in})$, where $X_{in}$ is the i-th individual data of $D$ and  j-th feature of $N$. After obtaining these points, these points are projected onto a hyperplane in $N+1$ dimensions to avoid situations where the data is non-linearly separable.
 In this case, using the kernel function below as the projection function for each data points in $D$ is a method of reducing the occurrence of non-linear separability:
$$\begin{bmatrix}x_1^{(2)} \\x_2^{(2)} \\... \\x_n^{(2)} \\ (\prod_{i=0}^{n} x_i)^{\frac{2}{n}} \end{bmatrix}$$
 After this step, we can find a $N+1$ dimensions hyperplane $w$ that can separate the binary class labels of $0$ and $1$ for the data points. With this hyperplane trained on the training data, we can extend it to classify future data points that do not have binary class labels. 
In \cite{santhanam2015application}, we can use genetic algorithms to achieve finding better hyperplanes. The following are the steps to find the hyperplane using a genetic algorithm:
Firstly, decide the level of generations ($l$), population size ($n$), variant ($v$), function constant ($b$), elite save rate ($p_e$), and mutations rate ($p_m$). Next, randomly select $N+1$ parameters of floating number between $0$ and $1$ in $w$, repeat it until $n$ hyperplanes are created.
In the second step, use $w^t \cdot x - b$ \cite{kumari2013classification} to compare the binary labels of the training data. If $w^t \cdot x - b > 0$, the output is $1$; if $w^t \cdot x - b < 0$, the output is $0$. This determines the accuracy of the $n$ hyperplanes.
Then, select the top $n \cdot p_e$ hyperplanes with high accuracy for crossover. The method is to take $v$ feature values from the parent chromosomes to replace or average (randomly) $v$ feature values from the mother chromosomes to create a new hyperplane. During the process, there is a probability of $p_m$ for random mutation of a feature value into a random floating number between $0$ and $1$. After mating $n-n \cdot p_e$ hyperplanes, return this step until the $l$th operation is completed and the best hyperplane is found.

@@

After the end of the iteration, multiply $T$ by $R_T$ and continue the iteration until the $T \le T_E$.Then, we get the approximate solution$f=f^*$.Every 2 iteration, the $T$ decreases and lower the probability of $f^{**}$ accepted as the solution.Stimulating annealing can avoid solution stuck at local minimum.Use neural network found by NAS, we can now predict with untrained data with $80\%$ or so accuracy.
\section{Naive Bayes classifier}

@@

\section{Experiment result}

\section{Conclusion}

\bibliographystyle{IEEEtran}
\bibliography{main}
\end{document}

>>>>

  \bf{neural network}: \rm{Neural} network have been used in many fields to deal with intricate datas.With input layer, hidden 
  layer and output layer constructed by neurons, each data in dataset is processed while passing through neurons, layer by layer. 
  After the processing, the outcome can be used to predict.Using back propogation, the accuracy of predictions increase in each 
  training. In order to construct the hidden layer more efficient, NAS(Neural Arcitecture Searching) is used to search suitable 
  structure for hidden layer, increasing the accuracy.According to \cite{Gadekallu2020}\cite{Beghriche2021}, many neural network 
  have been constructed and trained already, with high efficiency and accuracy in prediction of diabetes.

  \bf{naive Bayes classifier}: \rm{naive Bayes classifier} as its name suggest, is a machine learning method base on Bayesian 
  theorem, this model will statistic each data and find all conditional probability of each event occurring if each outcome holds. 
  And finally when it is asked to predict the result, the model will evaluate the data which requist provide and find the most 
  likely outcome according to the conditional probability it just recorded.

@@

\section{decision tree}
  Consider a dataset, $D$, which contains $N$ data and class label, the construction of a decision tree can be described as 
  below: suppose there are $M$ candidate decisions, denoted $f_i$. A decision can separate dataset $D$ into $m$ kinds, denote 
  $D'_j$. The decision tree will adopt $\arg\max_{f} G(D, f)=I(D)-\sum^m_{j=1}\frac{N'_j}{N}I(D'_j)$ as node decision, 
  and then recursively construct the tree until the data in separated dataset have the same class label. 
  When a data with unknown class label comes, a decision tree determines recursively by the decision node until the leaf node.
  The function of calculating information, $I$, can be various from implementation. The most famous two information function is 
  entropy, and gini impurity. The formula of information entropy is 
  \begin{equation}
    I_H(X)=-\sum_{x}p(x)\log_2p(x) 
  \end{equation}
  and gini impurity is 
  \begin{equation}
    I_G(X)=1-\sum_{x}p(x)^2
  \end{equation}

@@

\section{SVM}
  Given a dataset $D$ containing $N$ data points and a label with a binary class label of $0$ or $1$ representing the presence 
  or absence of diabetes, respectively. Individually project each data point in the dataset $D$ onto the hyperplane, we can obtain 
  a point $(X_{i1}, X_{i2}, ..., X_{ij}, ..., X_{in})$, where $X_{in}$ is the i-th individual data of $D$ and  j-th feature of $N$. 
  After obtaining these points, these points are projected onto a hyperplane in $N+1$ dimensions to avoid situations where the 
  data is non-linearly separable. 
  In this case, using the kernel function below as the projection function for each data points in $D$ is a method of reducing 
  the occurrence of non-linear separability: 
	$$\begin{bmatrix}x_1^{(2)} \\x_2^{(2)} \\... \\x_n^{(2)} \\ (\prod_{i=0}^{n} x_i)^{\frac{2}{n}} \end{bmatrix}$$
  After this step, we can find a $N+1$ dimensions hyperplane $w$ that can separate the binary class labels of $0$ and $1$ for 
  the data points. With this hyperplane trained on the training data, we can extend it to classify future data points that do 
  not have binary class labels. 
  Based on \cite{santhanam2015application}, we can use genetic algorithm (GA) to achieve finding better hyperplanes. The following are the 
  steps to find the hyperplane using a GA: Firstly, decide the level of generations ($l$), population size ($n$), 
  variant ($v$), function constant ($b$), elite save rate ($p_e$), and mutations rate ($p_m$). Next, randomly select $N+1$ parameters 
  of floating number between $0$ and $1$ in $w$, repeat it until $n$ hyperplanes are created. 
  In the second step, use $w^t \cdot x - b$ \cite{kumari2013classification} to compare the binary labels of the training data. If 
  $w^t \cdot x - b > 0$, the output is $1$; if $w^t \cdot x - b < 0$, the output is $0$. This determines the accuracy of the $n$ hyperplanes. 
  Then, select the top $n \cdot p_e$ hyperplanes with high accuracy for crossover. The method is to take $v$ feature values from 
  the parent chromosomes to replace or average (randomly) $v$ feature values from the mother chromosomes to create a new hyperplane. 
  During the process, there is a probability of $p_m$ for random mutation of a feature value into a random floating number between 
  $0$ and $1$. After mating $n-n \cdot p_e$ hyperplanes, return this step until the $l$th operation is completed and the best hyperplane 
  is found.

@@

  After the end of the iteration, multiply $T$ by $R_T$ and continue the iteration until the $T \le T_E$.Then, we get the approximate 
  solution$f=f^*$.Every 2 iteration, the $T$ decreases and lower the probability of $f^{**}$ accepted as the solution.Stimulating annealing 
  can avoid solution stuck at local minimum.Use neural network found by NAS, we can now predict with untrained data with $80\%$ or so accuracy.

\section{Naive Bayes classifier}
  Consider a dataset, $D$, which contain $M$ data points with $k$ class labels. The probability that a random data points belongs to 
  $i$-th class is $P(C_k\mid \bf{x})$ where $C_k$ is the event that data points $\bf{x}=(x_1,\cdots,x_n)$ belongs to $k$-th class.
  By using Bayes' theorem, the probability can be rewritten as 
  \begin{equation}
    \label{eqn:bayes}
    P(C_k\mid x)=\frac{P(C_k)P(\bf{x}\mid C_k)}{P(\bf{x})}
  \end{equation}
  In partice, 
  there is interest only in the numerator of that fraction, because the denominator does not depend on $C_k$ and the values of the 
  features that are given, so the denominator is effectively constant. 
  Then, by chain rule of conditional probability, the numerator of Eq. \ref{eqn:bayes} can be rewritten as
  \begin{equation}
    \label{eqn:rebayes}
    \begin{split}
      &P(C)P(x_1\mid C_k)P(x_2,\cdots,x_n\mid C_k,x_1)
      \\&=\cdots
      \\&=P(C)P(x_1\mid C_k)\cdots P(x_n\mid C_k,x_1,\cdots,x_{n-1})
    \end{split}
  \end{equation}

  Now assume that all features in $\bf{x}$ is mutually independent, $P(x_i\mid x_j, C_k)$ will be equal to $P(x_i\mid C_k)$. 
  Thus, the probability is 
  \begin{equation}
    \label{eqn:prob_classifier}
    P(C_k\mid x)=\frac{P(C_k)\prod^n_{i=1}P(x_i\mid C_k)}{Z}
  \end{equation}
  where $Z$ is a constant. 
  With Eq. \ref{eqn:prob_classifier}, a data points with unknown class label can be classified by choosing the most possible class: 
  \begin{equation}
    \label{eqn:classifier}
    \arg\max_k P(C_k)\prod^n_{i=1}P(x_i=x'_i\mid C_k)
  \end{equation}

  The problem is, when given is a continuous value instead of individual events, it need to be partitioned accroding to specific value 
  which below this value is an individual event while above is other evnet. However, the difficulty is how to find the best partition 
  that can fit the model best. By using gene alogrithm, the answer can be easily found. First, record maximum and minimum values of 
  given data in each dimension. Second, randomly partition data in each dimension according the maximum and minimum value recorded before 
  and repeat 100 times to generate enoguh species. Third, testing the accuracy of the model on the training data and keep top $K$ 
  good species and kill the rest. Then, let the these elites prodece offsprings, which means pass their partitions to offsprings. 
  When there is enough offsprings, all offsprings are going to have mutation, the partitions may slightly shift, 
  merge, split, disappear, or keep originally. Finally, repeat the whole iteration until found the partition that is close to optimal 
  solution after $T$ iterations.

@@

\section{Experiment result}
  This work compare the common classification algorithms, including KNN (with brute force, ANNOY-DFS, ANNOY-BFS), decision tree, 
  random forest, SVM (modified by GA), Neural Network, Naive Bayes classifier (modified by GA), PLA-pocket algorithm. 
  The programming language of KNN, decision tree, random forest and SVM-GA are C++20. And Neural Network, Naive Bayes classifier-GA 
  and PLA-pocket are using Python3 with pytorch and scikit-learn library. 
  Table \ref{table:overall} compares all datasets, which show that ...
  \begin{table*}[htb]
    %\normalsize
    %\centering
    \newcommand{\z}{\phantom{0}}
    \caption{\textsc{Comparison of Classification Techniques.}}
      \vspace{-\baselineskip}
    \begin{tabular}{@{}lccccccl@{}}\toprule
    Technique & Search (s) & testA & testA-normalized & testB & testB-normalized \\ \midrule
    KNN-Brute-Force  & $0.009$ & $76.6169 \pm \z{0}$                & $80.597 \pm 0$               & $78 \pm \z{0}$                 & $80 \pm \z{0}$\\
    KNN-ANNOY-DFS    & $0.003$ & $75.2438 \pm \z{1.8762}$           & $76.1294 \pm 2.0977$         & $74.9 \pm \z{2.5554}$          & $76.4 \pm \z{2.5377}$\\
    KNN-ANNOY-BFS    & $0.012$ & $76.6567 \pm \z{0.5340}$           & $80.597 \pm 0$               & $78.16 \pm \z{0.7310}$         & $80 \pm \z{0}$\\
    decision tree    & $0.009$ & $74.1294 \pm \z{0}$                & $74.1294 \pm 0$              & $76 \pm \z{0}$                 & $77 \pm \z{0}$\\
    random forest    & $0.004$ & $78.6965 \pm \z{1.751}$            & $78.5373 \pm 1.452$          & $77.98 \pm \z{2.083}$          & $77.5 \pm \z{2.516}$\\
    SVM-GA           & $X$ & $X \pm \z{X}$                          & $X \pm X$                    & $X \pm \z{X}$                  & $X \pm \z{X}$\\
    Neural Network   & $X$ & $X \pm \z{X}$                          & $X \pm X$                    & $X \pm \z{X}$                  & $X \pm \z{X}$\\
    Naive Bayes classifier-GA    & $X$ & $X \pm \z{X}$              & $X \pm X$                    & $X \pm \z{X}$                  & $X \pm \z{X}$\\
    PLA-pocket       & $X$ & $X \pm \z{X}$                          & $X \pm X$                    & $X \pm \z{X}$                  & $X \pm \z{X}$\\ \midrule
    %&& Search (s) & test & Search(s) & test & Search(s) & test \\ \midrule
    \end{tabular}
    \label{table:overall}
      \vspace{-\baselineskip}
  \end{table*}

\section{Conclusion}
  The experiment result shows that ...
\bibliographystyle{IEEEtran}
\bibliography{main}
\end{document}
